The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-09-12 analysis/paper/paper.qmd
Replace title_col with id_col
Update cleaning in data preparation script and package data

# Join text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")
```

@@

```{r pre-process-text}

meta_sw <- find_meta_stopwords(emu)
emu_sw <- urbanism_stopwords(
    add_stopwords = c("emu", "european post[\\-]?(graduate)?[\\s]?master[s]? in urbanism",
                      "tu delft", "ku leuven", "upc barcelona", "iuav venice"))
thesis_sw <- thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "figure", "ning"))
anonymisation_sw <- c("EMAIL_REMOVED", "AUTHOR_REMOVED", "FIRST_NAME_REMOVED", "LAST_NAME_REMOVED") |>
  paste(collapse = "|")
custom_sw <- c("space[s]?", "spatial", "plan", "(plann)\\w{0,}", "public", "development",
               "design", "process[es]?", "project[s]?", "figure[s]?", "map[s]?", "strateg(y|ies)", "intervention[s]?",
               "create", "exist", "analys(i|e)s") |>
  (\(.) paste0("\\b", ., "\\b"))() |> 
  paste(collapse = "|")

# Add cleaned text column
emu$text_clean <- emu$text_raw |> 
  # Remove text included with anonymisation
  str_remove_all(anonymisation_sw) |>
  # Remove white spaces and punctuation, and change text to lower-case
  clean_basic() |>
  # Remove title, subtitle and full title
  str_remove_all(meta_sw) |> 
  # Remove dataset-specific words
  str_remove_all(emu_sw) |>
  # Remove thesis-specific words
  str_remove_all(thesis_sw)

# Concatenate ngrams
emu$text_clean <- emu |> 
  c_ngrams(n_max = 3, text_col = "text_clean",
           id_col = "ID", min_freq = 20, lemma = TRUE)

# Words that were not included in ngrams are safe to remove now
emu$text_clean <- emu$text_clean |> 
  str_remove_all(custom_sw)

# # Get all concatenated ngrams
# unique(unlist(str_match_all(emu$text_clean, "[A-Za-z]+(?:_[A-Za-z]+)+")[1]))

# # Check if the word "space" was removed
# unique(unlist(str_match_all(emu$text_clean, "\\bspace\\b")))
# unique(unlist(str_match_all(emu$text_clean, "space(?:_[A-Za-z]+)+")))

@@

# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, title_col = "ID", top_n = 10)
```

>>>>

# Load cleaned text data
data(emu_clean)

# Join text with the metadata file  
emu <- emu_raw |> 
  left_join(emu_metadata, by = "ID") |> 
  left_join(emu_clean, by = "ID")
```

@@

@@

# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, id_col = "ID", top_n = 10)
```
